### 2023-04-05 application.tex
details

\begin{proof}
Recall that resilience is equivalent to  $\Bad \subseteq \pred^*(\Safe)$. For every pushdown automaton $A=(Q,\Sigma,...)$ and every regular language $L \subseteq Q \times \Sigma^*$, the set $\pred^*(L)$ is a computable regular language \cite{DBLP:journals/ipl/BouajjaniEFMRWW00}. Since $\Bad$ and $\Safe$ are both regular, we deduce that
%
%			Moreover, $post^*(\Bad)$ is also a computable regular language \alain{pourquoi ?}   $post^*(L)$ and
 the inclusion $\Bad \subseteq \pred^*(\Safe)$ is decidable and resilience too.
%
BRP
%
kRP
%
\end{proof}
%
Let us remark that $\uparrow \post^*(q,w)$ is also a computable regular language, but we cannot directly apply previous results on WSTS since pushdown automata are not WSTS for the usual orderings (subword, prefix).
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} for the subword ordering and $\uparrow \post^*$ is computable but context-free grammars are not strongly compatible.

@@

\begin{theorem}{}
Resilience is decidable for LCM, semilinear VASS, Integer VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
Resilience is decidable for lossy counter machines (LCM) with $\Safe$ and $\Bad$ semilinear sets as a consequence of Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that implies that $Pre^*(\Safe)$ is a computable semilinear set. Hence since the inclusion between two semilinear setsis decidable, we deduce that  $\Bad \subseteq \pred^*(\Safe)$ is decidable.

%		semilinear VASS.
 \alain{le plus simple serait que $\pred^*(L)$ is semilinear because $post^*(s)$ is semilinear , peut-être en inversant le VASS V en V'on aurait pred*(V)=post*(V') hence $post^*(L)$ is also semilinear ? hence pred ????}

>>>>

\begin{proof}
Recall that resilience is equivalent to  $\Bad \subseteq \pred^*(\Safe)$. For every pushdown automaton $A=(Q,\Sigma,...)$ and every regular language $L \subseteq Q \times \Sigma^*$, the set $\pred^*(L)$ is a computable regular language \cite{DBLP:journals/ipl/BouajjaniEFMRWW00}. Since $\Bad$ and $\Safe$ are both regular, we deduce that
%
%			Moreover, $post^*(\Bad)$ is also a computable regular language \alain{pourquoi ?}   $post^*(L)$ and
 the inclusion $\Bad \subseteq \pred^*(\Safe)$ is decidable and resilience too.
%
The BRP and the kRP are also decidable. The algorithm that computes $ \pred^*(\Safe)$ is polynomial. If $\Bad \subseteq \pred^*(\Safe)$ then one computes an integer $k$ such that the maximum of all minimal pathes that go from $\Bad$ to $\Safe$ is equal to $k$.\alain{à prouver}
%
\end{proof}
%
Let us remark that $\uparrow \post^*(q,w)$ is also a computable regular language, but we cannot directly apply previous results on WSTS since pushdown automata are not WSTS for the usual orderings (subword, prefix).
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} for the subword ordering and $\uparrow \post^*$ is computable but context-free grammars are not strongly compatible.

@@

\begin{theorem}{}
Resilience is decidable for  lossy counter machines, semilinear VASS, Integer VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

\begin{proof}
Resilience is decidable for lossy counter machines with $\Safe$ and $\Bad$ semilinear sets as a consequence of Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that implies that $\pred^*(\Safe)$ is a computable semilinear set. Hence since the inclusion between two semilinear sets is decidable, we deduce that  $\Bad \subseteq \pred^*(\Safe)$ is decidable.

%		semilinear VASS.
 \alain{le plus simple serait que $\pred^*(L)$ is semilinear because $\post^*(s)$ is semilinear , peut-être en inversant le VASS V en V'on aurait pred*(V)=post*(V') hence $post^*(L)$ is also semilinear ? hence pred ????}
